\newpage
\newsection{User Management}
\subsection{Aggregates}
\subsubsection{User}
\begin{itemize}
	\item \textbf{userId}: this attribute must be unique and refers to the \emph{user\_id} key in the corresponding \emph{Auth0} users table;
	\item \textbf{firstName}: user's first name;
	\item \textbf{lastName}: user's  last name;
	\item \textbf{date}: user's birth date;
	\item \textbf{email}: this attribute must be unique and respect the right format;
	\item External links:
	\begin{itemize}
		\item \textbf{role}: user's role;
		\item \textbf{group}: user's belonging group.
	\end{itemize}
\end{itemize}

\subsubsection{Role}
\begin{itemize}
	\item \textbf{roleId}: this attribute is generated with a UUID function;
	\item \textbf{name}: this attribute must be unique;
	\item \textbf{desc}: role's description;
	\item External links:
	\begin{itemize}
		\item \textbf{auth}: JSON array of role's authorizations.
	\end{itemize}
\end{itemize}

\subsubsection{Authorization}
\begin{itemize}
	\item \textbf{authId}: this attribute is generated with a UUID function;
	\item \textbf{name}: this attribute must be unique;
	\item \textbf{desc}: auth's description.
\end{itemize}

\subsubsection{Group}
\begin{itemize}
	\item \textbf{groupId}: this attribute is generated with a UUID function;
	\item \textbf{name}: this attribute must be unique;
	\item \textbf{desc}: group's description.
\end{itemize}

\subsection{Admin side}
\subsubsection{Authentication}
The authentication feature si provided by a third part provider, Auth0. In the admin side only admin users can log in; the user must be in the corresponding application's database on Auth0.
\subsubsection{Use cases}:
\begin{itemize}
	\item Creation of new aggregate object;
	\item Reading of aggregate object's info;
	\item Update of aggregate object;
	\item Delete an aggregate object;
	\item Recover the system state from a specific timestamp.
\end{itemize}
	

\subsection{User side}
\subsubsection{Authentication}
The authentication feature si provided by a third part provider, Auth0. In the user side only users can log in; it can sign in with email and password or using Google's authentication or just log in using its credentials.
\subsubsection{Use cases}:
\begin{itemize}
	\item Filling the users form to sign in into the User Management app;
	\item Update user's info;
	\item Reading user's info.
\end{itemize}

